### 2024-08-26 docs/manuscript.tex
Revised manuscript for clarity.

% The abstract could benefit from a clearer statement of the research question, methodology, and key findings. It currently mixes multiple ideas without a clear flow.
\Abstract{The development of accurate bioinformatic software tools is
  critical for the effective analysis of complex biological data. This
  study investigates the relationship between the academic department
  affiliations of authors and the accuracy of the bioinformatic tools
  they develop. By analyzing a corpus of previously benchmarked
  bioinformatic software tools, we mapped tools to academic fields of
  corresponding authors and evaluated tool accuracy by field. Our
  results indicate that "Medical Informatics," categorized under
  "Technologies," outperforms other fields in terms of software
  accuracy, with a mean proportion of wins in accuracy rankings higher
  than the null expectation. Conversely, tools developed by authors
  affiliated with "Bioinformatics" and "Engineering" fields produce
  lower accuracy tools. After correcting for multiple testing, no
  result is significant ($p>0.05$). Our findings show a distinct lack
  of an association between academic field and bioinformatic software
  accuracy, highlighting that the development of interdisciplinary
  software applications can be hosted by any aligned department with
  sufficient resources.  }

@@

Bioinformatics began gaining traction with the advent of
high-throughput sequencing technologies, necessitating robust
computational tools to handle the large amounts of data generated
\cite{Ouzounis:2003,hogeweg2011roots}. Departments specializing in
bioinformatics emerged from biology, computer science, and engineering
faculties, each contributing to the field's growth.

Bioinformatics inherently requires a multidisciplinary
approach. Interdisciplinary research allows for the integration of
methods and perspectives from different disciplines, leading to novel
insights and solutions that a single discipline might not achieve
independently \cite{mazzocchi2019scientific}.  This is especially
relevant in bioinformatics, where expertise in biological sciences is
crucial for understanding the data, while computational skills are
needed to develop and implement algorithms, and analyze and interpret
data.

The \textbf{biological and health sciences,} in particular genetics,
biochemistry and molecular biology provide essential domain knowledge,
ensuring that the software tools developed are biologically relevant
and accurate.  Biologists can identify the critical biological
questions and ensure that the computational tools are designed to
address these questions effectively. However, biology departments may
lack the advanced computational expertise required for sophisticated
software development. We have grouped the biological and health fields
into ``\textbf{domain experts}'' in the following analysis.

The \textbf{mathematical, engineering and computational sciences}, or
the ``\textbf{development experts}'' as we have dubbed them here,
contribute significantly by providing expertise in algorithm
development, data structures, and software engineering
principles. These skills are essential for creating efficient,
scalable, and robust bioinformatic tools. Nonetheless, the challenge
for computer science, engineering and mathematics or statistics
departments lies in acquiring a deep understanding of biological
domains necessary to ensure the relevance and accuracy of their
software tools.

Departmental differences might matter in the development of
bioinformatic software tools as they can reflect the the varying
expertise, resources, and perspectives that different academic fields
bring to the table. The development experts may excel in algorithm
efficiency, mathematical modelling, data handling and software engineering. However,
the domain experts may bring a deep understanding of biological
questions, data interpretation and limitations, and possibly better
curation of control datasets. As a result, the success of a tool may
depend more on the integration of diverse expertise rather than the
specific departmental affiliation of its developers. This blending of
skills could neutralize any potential disparities between departments,
leading to comparable outcomes regardless of the department of origin.

As the field of bioinformatics evolves, and the dependence on research
software tools increases due to growing data volumes, this study seeks
to determine whether the academic department of a corresponding author
is associated with the accuracy of the bioinformatic software tools
they develop. Specifically, we investigate whether the presumed
subject expertise, as indicated by the author's departmental
affiliation, has a measurable impact on the accuracy of these tools,
using a benchmarked corpus of bioinformatic software tools to assess
this relationship.

%% \textbf{Engineering}, particularly those focusing on
%% bioengineering and systems biology, bridge the gap between biological
%% sciences and computational techniques. They often have a strong
%% emphasis on interdisciplinary research, which is vital for
%% bioinformatics. These departments can leverage their strengths in both
%% domains to develop integrated solutions.

%% Nick Loman and Mick Watson (2013) argue that a good computational
%% biologist must understand both the biological questions and the
%% computational methods used to address them (Loman \& Watson
%% nbt.2740). This dual expertise is often best nurtured in departments
%% that prioritize interdisciplinary training and collaboration.

%% \textbf{The developer expert, domain expert or interdisciplinary scientist ...}

@@

We are interested in the relationship between the accuracy of
bioinformatic software tools and academic fields of study. Using a
published corpus of accuracy rankings for bioinformatic software
tools, we have mapped software tools to academic fields and evaluated
the relationship between software accuracy and academic field.

Previously benchmarked and collated accuracy ranks were obtained from
a published supplement \cite{gardner2024}. We mapped the corresponding
author addresses for published software tools to a standardised list of
specific ``fields of study'' \cite{fields2014}, we further grouped
these into higher level general fields, and broader areas of expertise
based on the address details of each corresponding author. The number
of tools representing each general and specific field is illustrated
in Figure~\ref{fig:fig1}. The majority of bioinformatic
software is produced by corresponding authors who list at least one of
Genetics, Bioinformatics or Computer Science or similar departments as
their primary address (Figure~\ref{fig:fig1}A). For general fields, the
Biological Sciences produce the bulk of software tools, followed by
the Computer Sciences (Figure~\ref{fig:fig1}B).

\begin{figure*}[ht!]
\begin{center}
  \includegraphics[width=0.8\textwidth]{forest-z-Plot.pdf}
\end{center}
\caption{(\textbf{A}) A forest plot, illustrating the mean and 95\%
  confidence intervals of the proportion of times software tools
  published by a given field ``win'' in pairwise
  comparisons. Confidence intervals and the mean was determined using
  a bootstrapping procedure. Within each field the entries have been
  sorted by the mean number of wins. The sample size for each field is
  indicated by the column of numbers on the right of the figure.
  (\textbf{B}) A Z-score was computed for each distribution of
  bootstrap samples for each field. The expected proportion of wins
  for randomly selected groups of tools was used as ``$x$''
  (i.e. null=0.5).   }
\label{fig:fig2}
\end{figure*}

The mean proportion of wins (e.g. if tool `A' outranks tool `B', this
is a win for tool `A') and the corresponding Z-scores give a way to
rank fields of study on the relative accuracy of bioinformatic
software benchmarked between 2005 and 2020 relative to the expected
number of wins for random groupings (i.e. $wins=0.5$). The greater the
proportion of wins, and $(-1)*Z-score$, then the more times tools from
a particular department outperformed competing tools in independent
benchmarks.

The specific and general fields that outperformed other
fields is ``Medical Informatics'' which is a branch of
``Technologies'', the same 16 software tools fall into both
fields. Five of which are different parameter options for the MAFFT
multiple sequence alignment tool \cite{katoh2008recent}.  These have a
mean proportion of wins of 0.70 and 95\% confidence interval of
$0.53-0.85$, which excludes the null of 0.5. The corresponding z-score
is $-1.88$ and $P=0.29$ after correcting for multiple testing.

At the other end of the spectrum is ``Bioinformatics'', ironically
authors that list ``Bioinformatics'' in their address field appear to
write less accurate software for bioinformatic
applications. The mean proportion of wins was 0.43, and 95\%
confidence interval of $0.33-0.53$. The corresponding z-score is
$1.20$ and $P=0.46$ after correcting for multiple
testing.

The general field ``Engineering'' also had a low rank. The mean
proportion of wins was just 0.34, and 95\% confidence interval of
$0.16-0.60$. The corresponding z-score is $1.25$. This general field
is made up of several smaller specific fields that includes
``Bioengineering and biomedical engineering'', ``Computer
engineering'' and ``Electrical and electronics engineering'' which
individually did not have more than ten corresponding software tools,
so were excluded from the more specific analysis.

The remaining general and specific academic fields have confidence
intervals that include the null value of 0.5, and relatively modest
z-scores that range from -0.49 to 0.96. The p-values for each were
greater than $0.05$.

For the highest level field classifications of software development
expert, biological domain expert or interdisciplinary expert each had
similar mean proportions of wins (0.51, 0.49 and 0.46
respectively). The interdisciplinary experts had a lower z-score of
$-0.87$, which corresponds to $P=0.46$ after correcting for multiple
testing.

@@

We have tested the assumption that the academic department subject
reflects the quality of research software. Our findings found no
significant association after multiple-testing correction between the
biological domain expert, the software developer expert or the
interdisciplinary scientist with software tool rankings on accuracy
measures. Leading us to conclude that assumptions regarding academic
department and bioinformatic software quality are likely false. The
general and specific research fields yielded similarly negative
results (Figure~\ref{fig:fig2}A).

Our earlier paper found that long-term commitments to updating
software was the leading factor associated with accurate software
tools. This current study complements that finding, showing that not
only do citation metrics (e.g. journal impact factors and author
H-index), tool age and tool speed, but also academic fields of inquiry
are \textbf{not} associated with prediction accuracy.

@@

%Limitations mentioned in the conclusion could be expanded to better discuss how they may affect the study's findings and their implications.

This study has several limitations. Some benchmarks rank several tool
options, the effects of which may be modest to large, and potentially
non-independent. The number of accuracy metrics used is also diverse,
some of which may be flawed in some circumstances. For example,
``accuracy'' with large class-imbalance \cite{luque2019impact}, or N50
which some commentators have criticised \cite{xie2021pdr}. Some
benchmarks are relatively small resulting in small changes in rank
having a potentially large impact on the proportion of wins. Finally,
the cohort of benchmarks has not been updated to include more recent
results.

There is likely a disconnect between training and the host department
for many bioinformatic tool developers. For example, this author
studied mathematics as an undergraduate, conducted a PhD in
bioinformatics, held postdoctoral fellowships in computer science and
molecular biology departments, spent several years at a genomics
research institute and is now employed in a Biochemistry
Department. The ``Biochemistry'' departmental label is not an accurate
reflection of my training or recent publications. I certainly can't
recall any of the key steps of glycolysis, the citric acid cycle or
the structure of any amino acid or protein.

The last, corresponding author is generally the principal investigator
leading a project. They may have limited involvement in the actual
development of any software tool while they (supposedly) provide
resources for the project and overall direction. However, there is a
significant overlap between the department of a first author, who
would generally be the primary developer of a tool, and the last
author (not tested here). Therefore we expect these results to be
broadly similar if first-author departments were used instead.

%OPen questions: what impact does training have on improving software quality?
%

%We end with echoing the call for more training and a continued 
%\cite{johanson2018software,siepel2019challenges}

@@

%The methodology section should provide more detail about how the software tools were selected and mapped to academic fields. It’s important to describe how biases or inconsistencies in mapping were addressed.
\textbf{Mapping tools to academic field:} For each software tool, when
available, the corresponding publication(s) were identified and the
addresses for the primary corresponding author were extracted
manually. In cases where an author lists multiple addresses, just the
first two are used. When multiple corresponding authors were listed,
the last corresponding author was selected.

The author department names were mapped to the closest associated
``fields of study'' listed by the National Science Foundation
\cite{fields2014}. We analysed fields at three different hierarchical
levels, firstly the specific fields (e.g. ``genetics'', ``computer
science'', ``bioinformatics'' etc). These are then mapped to more
general fields within the ``fields of study'' classification
(e.g. ``biological sciences'', ``computer sciences'' etc). We have
further mapped these to three expertise types, the \textbf{development
  experts}, \textbf{domain experts} and \textbf{interdisciplinary
  experts}. The development experts are from fields such as computer
science, mathematics and engineering, they are expected to bring
development-pertinent expertise in software engineering and
mathematical modeling of biological problems. The domain experts are
drawn from the biological and health sciences and are expected to have
detailed knowledge of the subject area and be invested in producing
high-performing software for their research. The interdisciplinary
experts are drawn from interdisciplinary subjects such as
bioinformatics, biostatistics and biomathematics. Additionally the
researchers who list both development and domain expertise in their
addresses (e.g. ``Computer Science'' and ``Genetics''). We have treated some fields as essentially synonymous, for
example departments of ``Computational Biology'' was mapped to
``Bioinformatics'', and ``Genomics'' is mapped to ``Genetics''.

@@

\textbf{Statistical analysis:} The accuracy data is derived from
benchmarks using a diverse number of metrics that include sensitivity,
specificity, PPV, FDR, error rates, AUROC, MCC and others
\cite{weber2019essential}. The number of tools ranked in any benchmark
ranged from 3 to 50. In order to obtain a representative measure of
accuracy for a field that transcends diverse accuracy measures and
numbers of ranked tools we elected to use ranks and a
bootstrapping strategy.  We randomly sample with replacement sets of
200 tools (from the total of 498), a benchmark that includes each tool
is selected at random and the number of times the tool ``won'' against
another tool is recorded, as is the total number of pairwise
comparisons that were made. These counts of wins and total comparisons
are transferred to the corresponding specific, general and expertise
areas. This is repeated 1,000 times, and allows a way to estimate the
mean proportions of wins allocated to each field, and a 95\%
confidence interval for this value (Figure~\ref{fig:fig2}A). We also compute a
Z-score for each field using the below equation. This measures the
number of standard deviations the mean number of wins is from the
expected null value of 0.5 for randomly grouped tools
(Figure~\ref{fig:fig2}B).

$z=\frac{x-\mu}{\sigma}$

%\textbf{WRITE UP: Bootstrapping, mean number of wins, confidence intervals, forest plot. }

@@

P-values are computed from the absolute value of the z-scores to
evaluate if any field is significantly distinguished from the null
i.e. $P[X > x]$. The P-values are corrected for multiple testing by
controlling the false discovery rate method
\cite{benjamini1995controlling}.

>>>>

% The abstract could benefit from a clearer statement of the research question, methodology, and key findings. It currently mixes multiple ideas without a clear flow.
\Abstract{
  The development of accurate bioinformatic software tools is crucial
  for the effective analysis of complex biological data. This study
  examines the relationship between the academic department
  affiliations of authors and the accuracy of the bioinformatic tools
  they develop. By analyzing a corpus of previously benchmarked
  bioinformatic software tools, we mapped bioinformatic tools to the
  academic fields of the corresponding authors and evaluated tool
  accuracy by field. Our results suggest that "Medical Informatics,"
  under the broader category of "Technologies," outperforms other
  fields in software accuracy, with a mean proportion of wins in
  accuracy rankings exceeding the null expectation. In contrast, tools
  developed by authors affiliated with "Bioinformatics" and
  "Engineering" fields tend to be less accurate. However, after
  correcting for multiple testing, none of the results are
  statistically significant ($p>0.05$). Our findings reveal no
  association between academic field and bioinformatic
  software accuracy, suggesting that the development of
  interdisciplinary software applications can be effectively
  undertaken by any department with sufficient resources and training.
}

@@

Bioinformatics gained significant traction with the advent of
high-throughput sequencing technologies, which created a need for
robust computational tools to manage the large volumes of data
generated \cite{Ouzounis:2003,hogeweg2011roots}. In response,
departments specializing in bioinformatics began to emerge from
biology, computer science, and engineering faculties, each bringing
unique contributions to the field's development and expansion.

The interdisciplinarity of bioinformatics enables the integration of
methods and perspectives from various disciplines, fostering novel
insights and solutions that might not be possible within a single
field \cite{mazzocchi2019scientific}. This requires a deep
understanding of biological sciences for interpreting
data, and strong computational skills are required to develop
algorithms and analyze the results at scale.

The \textbf{biological and health sciences,} in particular genetics,
biochemistry and molecular biology provide essential domain knowledge,
ensuring that the developed software tools are both biologically relevant
and accurate.  Biologists are well-positioned to identify critical biological
questions and ensure that computational tools are designed to
effectively address these. However, biology departments may
lack the advanced computational expertise required for developing sophisticated
software. In our analysis, we have grouped the biological and health fields
under the category of ``\textbf{domain experts}''.

The \textbf{mathematical, engineering and computational sciences},
referred to here as the ``\textbf{development experts}'', contribute
significantly by bringing expertise in algorithm development,
mathematical modelling, statistics, and software engineering
principles. These skills are essential for creating efficient,
scalable, and robust bioinformatic tools.  However, the challenge for
development experts is gaining a deep understanding of biological domains,
which is necessary to ensure software tools are both relevant
and accurate.

Departmental differences can influence the development of
bioinformatic software tools because they reflect the varying
expertise, resources, and perspectives that different academic fields
offer. Development experts may excel in areas such as algorithm
efficiency, mathematical modeling, data handling, and software
engineering, while domain experts may bring a deep understanding of
biological questions, data interpretation, limitations, and
potentially better curation of control datasets. Consequently, the
success of a tool may rely more on the integration of diverse
forms of expertise rather than the specific departmental affiliation
of its developers. This blending of skills can mitigate potential
disparities between departments, resulting in comparable outcomes
regardless of the department of origin.

As the field of bioinformatics evolves and reliance on research
software tools grows with increasing data volumes, this study aims to
determine whether the academic department of a corresponding author
influences the accuracy of the bioinformatic software tools they
develop. Specifically, we examine whether the presumed subject
expertise, reflected in the author's departmental affiliation, has a
measurable impact on tool accuracy, utilizing a benchmarked corpus of
bioinformatic software tools to evaluate this relationship.

@@

We are interested in exploring the relationship between the accuracy
of bioinformatic software tools and the academic fields of study of
their developers. Using a published corpus of accuracy rankings
for bioinformatic software tools, we mapped these tools to their
respective academic fields and evaluated how software accuracy
correlates with the developers' academic affiliations.

We obtained previously benchmarked and collated accuracy rankings from
a published supplement \cite{gardner2024}. Using these rankings, we
mapped the addresses of corresponding authors for each published
software tool to a standardized list of specific ``fields of study''
\cite{fields2014}. These fields were then grouped into higher-level
general fields and broader areas of expertise based on the address
details of each corresponding author. Figure~\ref{fig:fig1} illustrates
the number of tools representing each general and specific field. Most
bioinformatic software is developed by corresponding authors who list
Genetics, Bioinformatics, Computer Science, or similar departments as
their primary address (Figure~\ref{fig:fig1}A). Among the general fields,
the Biological Sciences produce the most software tools, followed by
the Computer Sciences (Figure~\ref{fig:fig1}B).

\begin{figure*}[ht!]
\begin{center}
  \includegraphics[width=0.8\textwidth]{forest-z-Plot.pdf}
\end{center}
\caption{(\textbf{A}) A forest plot, illustrating the mean and 95\%
  confidence intervals of the proportion of times software tools
  published by a given field ``win'' in pairwise
  comparisons. Confidence intervals and the mean was determined using
  a bootstrapping procedure. Within each field the entries have been
  sorted by the mean number of wins. The sample size for each field is
  indicated by the column of numbers on the right of the figure.
  (\textbf{B}) A Z-score was computed for each distribution of
  bootstrap samples for each field. The expected proportion of wins
  for randomly selected groups of tools was used as ``$x$''
  (i.e. null=0.5).}
\label{fig:fig2}
\end{figure*}

The mean proportion of wins (e.g., if tool `A' outranks tool `B', this
counts as a win for tool `A') and the corresponding Z-scores provide a
method to rank fields of study based on the relative accuracy of
bioinformatic software benchmarked between 2005 and 2020, compared to
the expected number of wins for random groupings (i.e., $wins =
0.5$). A higher proportion of wins and a greater $(-1) * Z-score$
indicate that tools from a particular department more frequently
outperformed competing tools in independent benchmarks.

The specific and general field that outperformed all others is
``Medical Informatics'', a branch of ``Technologies'', with 16
software tools categorized under both fields. Among these, five are
different parameter options for the MAFFT multiple sequence alignment
tool \cite{katoh2008recent}.  These Medical Informatic tools have a mean proportion of wins of
0.70 and 95\% confidence interval of $0.53-0.85$, which excludes the
null value of 0.5. The corresponding Z-score is $-1.88$, and after correcting for multiple testing, the P-value is $0.29$.

At the other end of the spectrum is ``Bioinformatics''. Ironically,
authors that list ``Bioinformatics'' in their address field tend to
produce less accurate software for bioinformatic applications. The
mean proportion of wins was 0.43, with a 95\% confidence interval of
$0.33-0.53$. The corresponding Z-score is $1.20$ and after correcting
for multiple testing the P-value is $0.46$.

The general field of ``Engineering'' also ranked low, with a mean
proportion of wins of just 0.34 and a 95\% confidence interval of
$0.16-0.60$. The corresponding Z-score is $1.25$. This general field
comprises several smaller specific fields, such as "Bioengineering and
Biomedical Engineering," "Computer Engineering," and "Electrical and
Electronics Engineering." However, since none of these specific fields
individually had more than ten corresponding software tools, they were
excluded from the more detailed analysis.

The remaining general and specific academic fields have confidence
intervals that include the null value of 0.5, and relatively modest
Z-scores that range from -0.49 to 0.96. The P-values for each were
greater than $0.05$.

For the highest level field classifications of software development
expert, biological domain expert or interdisciplinary expert each had
similar mean proportions of wins (0.51, 0.49 and 0.46
respectively). The interdisciplinary experts had a lower Z-score of
$-0.87$, which corresponds to $P=0.46$ after correcting for multiple
testing.

@@

We tested the assumption that the speciality of academic departments
reflect the quality of the research software they produce. Our
findings showed no significant association, after correcting for
multiple-testing, between the type of academic expertise -- whether
biological domain expert, software developer, or interdisciplinary
scientist -- and the accuracy rankings of bioinformatic software
tools. This leads us to conclude that assumptions linking academic
department affiliation to the quality of bioinformatic software are
likely incorrect. Similarly, both general and specific research fields
showed no significant associations (Figure~\ref{fig:fig2}).

Our earlier paper found that a long-term commitment to keeping
software updated was the primary factor associated with accurate
software tools. This current study complements that finding by demonstrating 
that citation metrics (e.g. journal impact factors and
author H-index), tool age, tool speed, and now academic fields of
inquiry are \textbf{not} associated with software accuracy.

@@

\textbf{Limitations:} Some benchmarks rank multiple tool options,
which can introduce modest to large effects as these options may not
be independent. Additionally, the accuracy metrics used are diverse,
and some may be flawed under certain conditions; for example,
``accuracy'' can be misleading with large class-imbalances
\cite{luque2019impact}, and the N50 metric for sequence assembly has
been criticized by some commentators \cite{xie2021pdr}. Moreover, some
benchmarks are relatively small, so even small changes in rank can
have a substantial impact on the proportion of wins for intermediate
rankings. Lastly, the cohort of benchmarks has not been updated to
include more recent results.

There is often a disconnect between a bioinformatic tool developer's
training and their host department. For example, the author of this
study completed an undergraduate degree in mathematics, a PhD in
bioinformatics, postdoctoral fellowships in computer science and
molecular biology departments, worked for several years at a genomics
research institute, and is currently employed in a Biochemistry
Department. The ``Biochemistry'' departmental label does not accurately
reflect the author's training or recent publications. In fact, the
author admits to not recalling key details of glycolysis, the citric
acid cycle, or the structures of amino acids and proteins.

The last, or corresponding, author is typically the principal
investigator who leads a project. They may have limited direct
involvement in the development of any software tool, while
their role is mainly to provide resources and overall direction for
the project. However, there is likely to be a significant overlap between the
department of the first author, who is usually the primary developer
of the tool, and the department of the last author (though this was
not tested in this study). Therefore, we expect that the results will
be broadly similar if first-author departments were analyzed instead.

%Open questions: what impact does training have on improving software quality?
%We could end with echoing the call for more training and a continued 
%e.g. \cite{johanson2018software,siepel2019challenges}

@@

%The methodology section should provide more detail about how the software tools were selected and mapped to academic fields. It’s important to describe how biases or inconsistencies in mapping were addressed.
\textbf{Mapping tools to academic field:} For each software tool, the
corresponding publication(s) were identified, and the addresses of the
primary corresponding author were manually extracted when
available. If an author listed multiple addresses, only the first two
were used. In cases with multiple corresponding authors, the last
corresponding author was chosen.

The department names of the authors were mapped to the closest
associated ``fields of study'' as defined by the National Science
Foundation \cite{fields2014}. We analysed these fields at three
hierarchical levels: first, specific fields (e.g. ``genetics'',
``computer science'', ``bioinformatics'' etc), which were then mapped
to broader general fields (e.g. ``biological sciences'', ``computer
sciences'' etc). Thirdly, we categorized them into three types of
expertise: \textbf{development experts}, \textbf{domain experts} and
\textbf{interdisciplinary experts}.  Development experts, from fields
such as computer science, mathematics, and engineering, are expected
to bring relevant expertise in software engineering and the
mathematical modeling of biological problems. Domain experts, from the
biological and health sciences, are anticipated to possess detailed
knowledge of their subject area and to be invested in producing
high-performing software for their research needs. Interdisciplinary
experts come from fields such as bioinformatics, biostatistics, and
biomathematics, and also include researchers who list both development
and domain expertise (e.g. ``Computer Science'' and ``Genetics''). We
have treated some fields as synonymous; for example, ``Computational
Biology'' was mapped to ``Bioinformatics'', and ``Genomics'' is mapped
to ``Genetics''.

@@

\textbf{Statistical analysis:} The accuracy data is derived from
benchmarks using a diverse number of metrics that include sensitivity,
specificity, PPV, FDR, error rates, AUROC, MCC and others
\cite{weber2019essential}. The number of tools ranked in any benchmark
ranged from 3 to 50. In order to obtain a representative measure of
accuracy for a field that accounts for the diversity in accuracy measures and
number of ranked tools, we employed a rank-based and
bootstrapping strategy.
We randomly sampled, with replacement, sets of 200 tools from the total of 498 tools. For each tool, a corresponding benchmark was selected at random, and the number of times the tool ``won'' against another tool was recorded, along with the total number of pairwise comparisons made. These counts of wins and total comparisons were then assigned to the corresponding specific, general, and expertise areas. This process was repeated 1,000 times to estimate the mean proportions of wins for each field, along with a 95\% confidence interval for these values (Figure~\ref{fig:fig2}A).
Additionally, we calculated a Z-score for each field to determine the number of standard deviations the mean number of wins deviates from the expected null value of 0.5 for randomly grouped tools
(Figure~\ref{fig:fig2}B).

$Z-score=\frac{x-\mu}{\sigma}$

@@

P-values are computed from the absolute value of the Z-scores to
evaluate if any field is significantly distinguished from the null
i.e. $P[X > x]$. The P-values are corrected for multiple testing by
controlling the false discovery rate method
\cite{benjamini1995controlling}.
